Carbonate chemistry at Ny-Ålesund

### 2023-02-14 awipev-CO2.Rmd
boron estimated according to Lee et al. (2010)

pH_seafet <- pH_seafet %>% 
  dplyr::mutate(
    ph_s_sf_temp_insi = pHinsi(pH = pH_seafet$ph_s_sf, 
                         ALK = pH_seafet$at_mean_interp*1e-6, 
                         Tinsi = pH_seafet$temp_insitu_11m_mix_interp, 
                         Tlab = pH_seafet$temp_s_lab, Pinsi = 11/10, 
                         S = pH_seafet$sal_fb_mix_interp, Pt = 0, Sit = 0, 
                         k1k2 = "l", kf = "dg", ks="d", 
                         pHscale = "T", b="u74"),
   ph_s_sf_temp_4 = pHinsi(pH = pH_seafet$ph_s_sf, # with Lueker
                         ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = 4, 
                         Tlab = pH_seafet$temp_s_lab, Pinsi = 11/10, 
                         S = pH_seafet$sal_fb_mix_interp, Pt = 0, Sit = 0, 
                         k1k2 = "l", kf = "dg", ks="d", 
                         pHscale = "T", b="u74")
  )
# Conversion of spec pH of FerryBox samples to FerryBox temp
pH_durafet <- d %>%
  tidyr::drop_na(ph_s_dur, sal_fb, temp_fb)
pH_durafet <- pH_durafet %>% 
  dplyr::mutate(
    ph_s_dur_temp_fb = pHinsi(pH = pH_durafet$ph_s_dur, 
                              ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = pH_durafet$temp_fb, 
                              Tlab = pH_durafet$temp_s_lab, Pinsi = 0, S = pH_durafet$sal_fb, 
                              Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74"),
    ph_s_dur_temp_4 = pHinsi(pH = pH_durafet$ph_s_dur,
                             ALK = pH_durafet$at_mean_interp * 1e-6, Tinsi = 4,
                             Tlab = pH_durafet$temp_s_lab, Pinsi = 0,
                             S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "l", 
                             kf = "dg", ks = "d",
                             pHscale = "T", b = "u74")
   )

@@

# pH calculated (at and ct) at Ferrybox sal and temp
discrete_no_na <- discrete %>%
  dplyr::filter(!is.na(sal_fb)  & !is.na(temp_fb) & !is.na(at) & !is.na(ct))
discrete_is_na <- discrete %>%
  dplyr::filter(is.na(sal_fb)  | is.na(temp_fb) | is.na(at) | is.na(ct))
carb <- carb(15, discrete_no_na$at_mean_interp*1e-6, discrete_no_na$ct_mean_interp*1e-6, S = discrete_no_na$sal_fb, T = discrete_no_na$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
discrete_no_na$ph_calc_fb <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
discrete_no_na$pco2_calc_fb <- carb$pCO2

@@

# normalized seafet pH 4°C and remove sf biofouling period
tmp <- d_all %>%
  dplyr::select(datetime, depth, at, sal_insitu_ctd_mix, temp_sf, pHint_tot_sf) %>%
  tidyr::drop_na() %>%
  dplyr::filter(datetime < as.POSIXct("2018-01-01") | datetime > as.POSIXct("2018-02-03"))
tmp$pHint_tot_sf_temp_4 <- seacarb::pHinsi(pH=tmp$pHint_tot_sf, ALK=mean(tmp$at*1e-6, na.rm = TRUE), Tinsi=4, Tlab=tmp$temp_sf, Pinsi=tmp$depth/10, S=tmp$sal_insitu_ctd_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
d_all <- d_all %>% 
  left_join(tmp %>% dplyr::select(datetime, pHint_tot_sf_temp_4), by="datetime")
```

@@

```{r durafet clean up, echo=FALSE, message= FALSE, warning=FALSE}
d_all <- d_all %>% 
  dplyr::mutate(pH_dur = ph_dur_corr) %>% # the right durafet pH at in situ temp from now on
  dplyr::select(-ph_dur, -ph_dur_corr)
# normalized durafet pH 4°C
tmp <- d_all %>%
  dplyr::select(datetime, at, sal_fb_mix, temp_fb, pH_dur) %>%
  tidyr::drop_na()
tmp$pH_dur_temp_4 <- seacarb::pHinsi(pH=tmp$pH_dur, ALK=tmp$at, Tinsi=4, Tlab=tmp$temp_fb, Pinsi=11/10, S=tmp$sal_fb_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
d_all <- d_all %>% 
  left_join(tmp %>% dplyr::select(datetime, pH_dur_temp_4), by="datetime")
```

@@

```{r, echo=FALSE, message= FALSE, warning=FALSE}
# Normalize pH_calc from AT/CT to 4°c
tmp <- discrete %>%
  dplyr::select(datetime, sal_fb_mix, temp_fb, ph_calc_fb, at) %>%
  tidyr::drop_na()
tmp$pH_calc_fb_temp_4 <- pHinsi(pH = tmp$ph_calc_fb, ALK=tmp$at*1e-6, Tinsi=4, Tlab=tmp$temp_fb, Pinsi=11/10, S=tmp$sal_fb_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")

@@

# Effects of changes in po4 and si
# 1st cakculate mean values
means <- d_all %>% 
  group_by(montht) %>% 
  summarize(mean_ct = mean(ct, na.rm = TRUE),
            mean_at_calc = mean(at_calc, na.rm = TRUE),
            mean_pco2_calc = mean(pco2_calc_fb, na.rm = TRUE),
            mean_sal = mean(sal_fb_mix, na.rm = TRUE),
            mean_temp = mean(temp_fb, na.rm = TRUE)) %>% 
  ungroup()
mean_ct <-  mean(means$mean_ct)
mean_at_calc <-  mean(means$mean_at_calc)
mean_pco2_calc <-  mean(means$mean_pco2_calc)
mean_sal <-  mean(means$mean_sal)
mean_temp <-  mean(means$mean_temp)
# then check impacts of 0, min and max nutrient values using pco2 and AT
carb_po4_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = c(0, min(d_all$po4/1e6, na.rm = TRUE), max(d_all$po4/1e6, na.rm = TRUE)), Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_po4_0a <- carb_po4_1[1,] - carb_po4_1[3,] # diff between no PO4 and max PO4
diff_po4_1a <- carb_po4_1[2,] - carb_po4_1[3,] # diff between min PO4 and max PO4
carb_Si_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0,
                Pt = 0, Sit = c(0, min(d_all$si/1e6, na.rm = TRUE), max(d_all$si/1e6, na.rm = TRUE)), 
                k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_Si_0a <- carb_Si_1[1,] - carb_Si_1[3,] # diff between no Si and max Si
diff_Si_1a <- carb_Si_1[2,] - carb_Si_1[3,] # diff between no Si and max Si
# then check impacts of O, min and max nutrient values using AT-DIC pair
carb_po4_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = c(0, min(d_all$po4/1e6, na.rm = TRUE), max(d_all$po4/1e6, na.rm = TRUE)), Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_po4_0b <- carb_po4_2[1,] - carb_po4_2[3,] # diff between no PO4 and max PO4
diff_po4_1b <- carb_po4_2[2,] - carb_po4_2[3,] # diff between min PO4 and max PO4
carb_Si_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
                Pt = 0, Sit = c(0, min(d_all$si/1e6, na.rm = TRUE), max(d_all$si/1e6, na.rm = TRUE)), 
                k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_Si_0b <- carb_Si_2[1,] - carb_Si_2[3,] # diff between no Si and max Si
diff_Si_1b <- carb_Si_2[2,] - carb_Si_2[3,] # diff between no Si and max Si
# then check impacts of O, max PO4 and NO3 values using pCO2 and AT as well as AT-DIC pair
carb_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = c(0, max(d_all$po4/1e6, na.rm = TRUE)), Sit = c(0, max(d_all$si/1e6, na.rm = TRUE)),
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
carb_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = c(0, max(d_all$po4/1e6, na.rm = TRUE)), Sit = c(0, max(d_all$si/1e6, na.rm = TRUE)),
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_max_0a <- carb_1[1,] - carb_1[2,] # pco2-AT: diff between (0 PO4 and Si) and (max PO4 and Si)
diff_max_0b <- carb_2[1,] - carb_2[2,] # AT-CT: diff between (0 PO4 and Si) and (max PO4 and Si)

@@

# calculate typical uncertainty assuming uncertainties of 3 uatm for pCO2 and 4 umol/kg for AT and CT
errors_pco2_at <- seacarb::errors(flag=24, var1=mean_pco2, var2=1e-6*mean_at, S=mean_sal,
                          T=mean_temp, P=0, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T",
                          b="u74", evar1=3, evar2 = 4e-6)
errors_at_ct <- seacarb::errors(flag=15, var1=1e-6*mean_at, var2=1e-6*mean_ct, S=mean_sal,
                          T=mean_temp, P=0, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T",
                          b="u74", evar1=4e-6, evar2 = 4e-6)
errors <- tibble(
  flag = c("pCO2-AT", "AT-CT"),
  S = c(mean_discrete$mean_sal, mean_discrete$mean_sal),
  T = c(mean_discrete$mean_temp, mean_discrete$mean_temp),
  pco2 = c(mean_discrete$mean_pco2, NA),
  CT = c(NA, mean_discrete$mean_ct),
  AT = c(mean_discrete$mean_at, mean_discrete$mean_at),
  e_pH = c(errors_pco2_at$pH, errors_at_ct$pH),
  e_pCO2 = c(NA, errors_at_ct$pCO2),
  e_DIC = c(errors_pco2_at$pH, NA) * 1e3,
  e_Oa = c(errors_pco2_at$OmegaAragonite, errors_at_ct$OmegaAragonite
  )
)

# # impacts using pco2 and AT pair
# carb_l_1 <- carb(24, mean_pco2, mean_at*1e-6, S = mean_sal, T = mean_temp, P = 0, 
#                  Pt = 0, Sit = 0,
#                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
# carb_s_1 <- carb(24, mean_pco2, mean_at*1e-6, S = mean_sal, T = mean_temp, P = 0, 
#                  Pt = 0, Sit = 0,
#                  k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
# diff_ls_1 <- carb_l_1 - carb_s_1
# # impacts using AT-CT pair
# carb_l_2 <- carb(15, mean_at*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
#                  Pt = 0, Sit = 0,
#                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
# carb_s_2 <- carb(15, mean_at*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
#                 Pt = 0, Sit = 0, 
#                 k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
# diff_ls_2 <- carb_l_2 - carb_s_2
# summary
```

@@

                         pHscale = "T", b="u74"),

@@

                         pHscale = "T", b="u74"),       # Millero 02

@@

                         pHscale = "T", b="u74")

@@

               pHscale = "T", b = "u74")

@@

```{r, echo=FALSE, message= FALSE, warning=FALSE}
# we look at pCO2 NOT normalized at 4°C at all depths
# calculate pCO2 from pH and salinity-derived AT
tmp <- d_all %>%
  dplyr::select(datetime,
                montht,
                depth_group,
                depth,
                pHint_tot_sf,
                sal_insitu_ctd,
                temp_insitu_ctd) %>%
  drop_na() %>%
  dplyr::mutate(
    at_remos = (intercept_s_at + slope_s_at * sal_insitu_ctd) * 1e-6,
    pco2_remos_ctd_temp = seacarb::carb(
      flag = 8,
      var1 = pHint_tot_sf,
      var2 = at_remos,
      S = sal_insitu_ctd,
      T = temp_insitu_ctd,
      Patm = 1,
      P = depth / 10,
      Pt = 0,
      Sit = 0,
      k1k2 = "l",
      kf = "dg",
      ks = "d",
      pHscale = "T",
      b = "u74"
    )$pCO2
  )
# add at_remos and pco2_remos_ctd_temp to d_all
d_all <-
  dplyr::left_join(d_all, dplyr::select(tmp, datetime, at_remos, pco2_remos_ctd_temp), by = "datetime") %>%
  dplyr::select(sort(everything()))
tmp <- tmp %>% 
  dplyr::select(montht, pco2_remos_ctd_temp, depth_group) %>%
  dplyr::filter(depth_group != "NA") %>% 
  dplyr::mutate(depth_group = factor(depth_group, levels = depth_labels))
p <- tmp %>% 
  ggplot(aes(x=as.factor(depth_group), y = pco2_remos_ctd_temp)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "pco2_sf vs depth", x = "Depth (m)", y= "fCO2 (uatm)") +
  scale_x_discrete(labels = depth_labels) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
summary(aov(tmp$pco2_remos_ctd_temp ~ tmp$depth_group * tmp$montht))

@@

```{r, include=FALSE}
# First we prepare data. CT is needed for deconvolution
# we calculate it from at_calc and pCO2
# nuts are not taken into consideration
deconv_tmp <- d_all %>% # just for this chunk
  dplyr::select(datetime, monthd, sal_fb_mix, temp_fb, pco2_fb, at_calc) %>% 
  tidyr::drop_na()
deconv_tmp <- deconv_tmp %>% 
  dplyr::mutate(ct_calc = seacarb::carb(
    flag = 24, var1 = deconv_tmp$pco2_fb, var2 = deconv_tmp$at_calc*1e-6, S=deconv_tmp$sal_fb_mix, T=deconv_tmp$temp_fb, 
    Patm=1, P=1.1, Pt=0, Sit=0, 
    k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$DIC * 1e6
    )
deconv_monthly <-  deconv_tmp %>% 
  dplyr::group_by(monthd) %>% 
  dplyr::summarise(
    sal_fb_mix = mean(sal_fb_mix, na.rm = TRUE),
    temp_fb = mean(temp_fb, na.rm = TRUE),
    pco2_fb = mean(pco2_fb, na.rm = TRUE),
    at_calc = mean(at_calc, na.rm = TRUE),
    ct_calc = mean(ct_calc, na.rm = TRUE)
  ) %>% 
  dplyr::ungroup()

@@

```{r, fig.width=10, fig.height=10, echo=FALSE, message= FALSE, warning = FALSE}
# we calculate it from at_calc and pCO2
# nuts are not taken into consideration
tmp <- d_all %>% # just for this chunk
  dplyr::select(datetime, monthd, sal_fb_mix, temp_fb, pco2_fb, at_calc) %>% 
  tidyr::drop_na() %>% 
  dplyr::mutate(OmegaAragonite = seacarb::carb(
    flag = 24, var1 = pco2_fb, var2 = at_calc*1e-6, S=sal_fb_mix, T=temp_fb, 
    Patm=1, P=1.1, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$OmegaAragonite)
summary(tmp$OmegaAragonite)
#plot
size_point <- 0.3 # size of data points
alpha <- 1 #transparency
size_labs <- 6 # font size labels

>>>>

pH_seafet <- pH_seafet %>% 
  dplyr::mutate(
    ph_s_sf_temp_insi = pHinsi(pH = pH_seafet$ph_s_sf, 
                         ALK = pH_seafet$at_mean_interp*1e-6, 
                         Tinsi = pH_seafet$temp_insitu_11m_mix_interp, 
                         Tlab = pH_seafet$temp_s_lab, Pinsi = 11/10, 
                         S = pH_seafet$sal_fb_mix_interp, Pt = 0, Sit = 0, 
                         k1k2 = "l", kf = "dg", ks="d", 
                         pHscale = "T", b="l10"),
   ph_s_sf_temp_4 = pHinsi(pH = pH_seafet$ph_s_sf, # with Lueker
                         ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = 4, 
                         Tlab = pH_seafet$temp_s_lab, Pinsi = 11/10, 
                         S = pH_seafet$sal_fb_mix_interp, Pt = 0, Sit = 0, 
                         k1k2 = "l", kf = "dg", ks="d", 
                         pHscale = "T", b="l10")
  )
# Conversion of spec pH of FerryBox samples to FerryBox temp
pH_durafet <- d %>%
  tidyr::drop_na(ph_s_dur, sal_fb, temp_fb)
pH_durafet <- pH_durafet %>% 
  dplyr::mutate(
    ph_s_dur_temp_fb = pHinsi(pH = pH_durafet$ph_s_dur, 
                              ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = pH_durafet$temp_fb, 
                              Tlab = pH_durafet$temp_s_lab, Pinsi = 0, S = pH_durafet$sal_fb, 
                              Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="l10"),
    ph_s_dur_temp_4 = pHinsi(pH = pH_durafet$ph_s_dur,
                             ALK = pH_durafet$at_mean_interp * 1e-6, Tinsi = 4,
                             Tlab = pH_durafet$temp_s_lab, Pinsi = 0,
                             S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "l", 
                             kf = "dg", ks = "d",
                             pHscale = "T", b = "l10")
   )

@@

# pH calculated (at and ct) at Ferrybox sal and temp
discrete_no_na <- discrete %>%
  dplyr::filter(!is.na(sal_fb)  & !is.na(temp_fb) & !is.na(at) & !is.na(ct))
discrete_is_na <- discrete %>%
  dplyr::filter(is.na(sal_fb)  | is.na(temp_fb) | is.na(at) | is.na(ct))
carb <- carb(15, discrete_no_na$at_mean_interp*1e-6, discrete_no_na$ct_mean_interp*1e-6, S = discrete_no_na$sal_fb, T = discrete_no_na$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "l10")
discrete_no_na$ph_calc_fb <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
discrete_no_na$pco2_calc_fb <- carb$pCO2

@@

# normalized seafet pH 4°C and remove sf biofouling period
tmp <- d_all %>%
  dplyr::select(datetime, depth, at, sal_insitu_ctd_mix, temp_sf, pHint_tot_sf) %>%
  tidyr::drop_na() %>%
  dplyr::filter(datetime < as.POSIXct("2018-01-01") | datetime > as.POSIXct("2018-02-03"))
tmp$pHint_tot_sf_temp_4 <- seacarb::pHinsi(pH=tmp$pHint_tot_sf, ALK=mean(tmp$at*1e-6, na.rm = TRUE), Tinsi=4, Tlab=tmp$temp_sf, Pinsi=tmp$depth/10, S=tmp$sal_insitu_ctd_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="l10")
d_all <- d_all %>% 
  left_join(tmp %>% dplyr::select(datetime, pHint_tot_sf_temp_4), by="datetime")
```

@@

```{r durafet clean up, echo=FALSE, message= FALSE, warning=FALSE}
d_all <- d_all %>% 
  dplyr::mutate(pH_dur = ph_dur_corr) %>% # the right durafet pH at in situ temp from now on
  dplyr::select(-ph_dur, -ph_dur_corr)
# normalized durafet pH 4°C
tmp <- d_all %>%
  dplyr::select(datetime, at, sal_fb_mix, temp_fb, pH_dur) %>%
  tidyr::drop_na()
tmp$pH_dur_temp_4 <- seacarb::pHinsi(pH=tmp$pH_dur, ALK=tmp$at, Tinsi=4, Tlab=tmp$temp_fb, Pinsi=11/10, S=tmp$sal_fb_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="l10")
d_all <- d_all %>% 
  left_join(tmp %>% dplyr::select(datetime, pH_dur_temp_4), by="datetime")
```

@@

```{r, echo=FALSE, message= FALSE, warning=FALSE}
# Normalize pH_calc from AT/CT to 4°c
tmp <- discrete %>%
  dplyr::select(datetime, sal_fb_mix, temp_fb, ph_calc_fb, at) %>%
  tidyr::drop_na()
tmp$pH_calc_fb_temp_4 <- pHinsi(pH = tmp$ph_calc_fb, ALK=tmp$at*1e-6, Tinsi=4, Tlab=tmp$temp_fb, Pinsi=11/10, S=tmp$sal_fb_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="l10")

@@

# Effects of changes in po4 and si
# 1st cakculate mean values
means <- d_all %>% 
  group_by(montht) %>% 
  summarize(mean_ct = mean(ct, na.rm = TRUE),
            mean_at_calc = mean(at_calc, na.rm = TRUE),
            mean_pco2_calc = mean(pco2_calc_fb, na.rm = TRUE),
            mean_sal = mean(sal_fb_mix, na.rm = TRUE),
            mean_temp = mean(temp_fb, na.rm = TRUE)) %>% 
  ungroup()
mean_ct <-  mean(means$mean_ct)
mean_at_calc <-  mean(means$mean_at_calc)
mean_pco2_calc <-  mean(means$mean_pco2_calc)
mean_sal <-  mean(means$mean_sal)
mean_temp <-  mean(means$mean_temp)
# then check impacts of 0, min and max nutrient values using pco2 and AT
carb_po4_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = c(0, min(d_all$po4/1e6, na.rm = TRUE), max(d_all$po4/1e6, na.rm = TRUE)), Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "l10")
diff_po4_0a <- carb_po4_1[1,] - carb_po4_1[3,] # diff between no PO4 and max PO4
diff_po4_1a <- carb_po4_1[2,] - carb_po4_1[3,] # diff between min PO4 and max PO4
carb_Si_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0,
                Pt = 0, Sit = c(0, min(d_all$si/1e6, na.rm = TRUE), max(d_all$si/1e6, na.rm = TRUE)), 
                k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "l10")
diff_Si_0a <- carb_Si_1[1,] - carb_Si_1[3,] # diff between no Si and max Si
diff_Si_1a <- carb_Si_1[2,] - carb_Si_1[3,] # diff between no Si and max Si
# then check impacts of O, min and max nutrient values using AT-DIC pair
carb_po4_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = c(0, min(d_all$po4/1e6, na.rm = TRUE), max(d_all$po4/1e6, na.rm = TRUE)), Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "l10")
diff_po4_0b <- carb_po4_2[1,] - carb_po4_2[3,] # diff between no PO4 and max PO4
diff_po4_1b <- carb_po4_2[2,] - carb_po4_2[3,] # diff between min PO4 and max PO4
carb_Si_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
                Pt = 0, Sit = c(0, min(d_all$si/1e6, na.rm = TRUE), max(d_all$si/1e6, na.rm = TRUE)), 
                k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "l10")
diff_Si_0b <- carb_Si_2[1,] - carb_Si_2[3,] # diff between no Si and max Si
diff_Si_1b <- carb_Si_2[2,] - carb_Si_2[3,] # diff between no Si and max Si
# then check impacts of O, max PO4 and NO3 values using pCO2 and AT as well as AT-DIC pair
carb_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = c(0, max(d_all$po4/1e6, na.rm = TRUE)), Sit = c(0, max(d_all$si/1e6, na.rm = TRUE)),
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "l10")
carb_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = c(0, max(d_all$po4/1e6, na.rm = TRUE)), Sit = c(0, max(d_all$si/1e6, na.rm = TRUE)),
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "l10")
diff_max_0a <- carb_1[1,] - carb_1[2,] # pco2-AT: diff between (0 PO4 and Si) and (max PO4 and Si)
diff_max_0b <- carb_2[1,] - carb_2[2,] # AT-CT: diff between (0 PO4 and Si) and (max PO4 and Si)

@@

# calculate typical uncertainty assuming uncertainties of 3 uatm for pCO2 and 4 umol/kg for AT and CT
errors_pco2_at <- seacarb::errors(flag=24, var1=mean_pco2, var2=1e-6*mean_at, S=mean_sal,
                          T=mean_temp, P=0, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T",
                          b="l10", evar1=3, evar2 = 4e-6)
errors_at_ct <- seacarb::errors(flag=15, var1=1e-6*mean_at, var2=1e-6*mean_ct, S=mean_sal,
                          T=mean_temp, P=0, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T",
                          b="l10", evar1=4e-6, evar2 = 4e-6)
errors <- tibble(
  flag = c("pCO2-AT", "AT-CT"),
  S = c(mean_discrete$mean_sal, mean_discrete$mean_sal),
  T = c(mean_discrete$mean_temp, mean_discrete$mean_temp),
  pco2 = c(mean_discrete$mean_pco2, NA),
  CT = c(NA, mean_discrete$mean_ct),
  AT = c(mean_discrete$mean_at, mean_discrete$mean_at),
  e_pH = c(errors_pco2_at$pH, errors_at_ct$pH),
  e_pCO2 = c(NA, errors_at_ct$pCO2),
  e_DIC = c(errors_pco2_at$pH, NA) * 1e3,
  e_Oa = c(errors_pco2_at$OmegaAragonite, errors_at_ct$OmegaAragonite
  )
)

# # impacts using pco2 and AT pair
# carb_l_1 <- carb(24, mean_pco2, mean_at*1e-6, S = mean_sal, T = mean_temp, P = 0, 
#                  Pt = 0, Sit = 0,
#                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "l10")
# carb_s_1 <- carb(24, mean_pco2, mean_at*1e-6, S = mean_sal, T = mean_temp, P = 0, 
#                  Pt = 0, Sit = 0,
#                  k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "l10")
# diff_ls_1 <- carb_l_1 - carb_s_1
# # impacts using AT-CT pair
# carb_l_2 <- carb(15, mean_at*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
#                  Pt = 0, Sit = 0,
#                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "l10")
# carb_s_2 <- carb(15, mean_at*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
#                 Pt = 0, Sit = 0, 
#                 k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "l10")
# diff_ls_2 <- carb_l_2 - carb_s_2
# summary
```

@@

                         pHscale = "T", b="l10"),

@@

                         pHscale = "T", b="l10"),       # Millero 02

@@

                         pHscale = "T", b="l10")

@@

               pHscale = "T", b = "l10")

@@

```{r, echo=FALSE, message= FALSE, warning=FALSE}
# we look at pCO2 NOT normalized at 4°C at all depths
# calculate pCO2 from pH and salinity-derived AT
tmp <- d_all %>%
  dplyr::select(datetime,
                montht,
                depth_group,
                depth,
                pHint_tot_sf,
                sal_insitu_ctd,
                temp_insitu_ctd) %>%
  drop_na() %>%
  dplyr::mutate(
    at_remos = (intercept_s_at + slope_s_at * sal_insitu_ctd) * 1e-6,
    pco2_remos_ctd_temp = seacarb::carb(
      flag = 8,
      var1 = pHint_tot_sf,
      var2 = at_remos,
      S = sal_insitu_ctd,
      T = temp_insitu_ctd,
      Patm = 1,
      P = depth / 10,
      Pt = 0,
      Sit = 0,
      k1k2 = "l",
      kf = "dg",
      ks = "d",
      pHscale = "T",
      b = "l10"
    )$pCO2
  )
# add at_remos and pco2_remos_ctd_temp to d_all
d_all <-
  dplyr::left_join(d_all, dplyr::select(tmp, datetime, at_remos, pco2_remos_ctd_temp), by = "datetime") %>%
  dplyr::select(sort(everything()))
tmp <- tmp %>% 
  dplyr::select(montht, pco2_remos_ctd_temp, depth_group) %>%
  dplyr::filter(depth_group != "NA") %>% 
  dplyr::mutate(depth_group = factor(depth_group, levels = depth_labels))
p <- tmp %>% 
  ggplot(aes(x=as.factor(depth_group), y = pco2_remos_ctd_temp)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "pco2_sf vs depth", x = "Depth (m)", y= "fCO2 (uatm)") +
  scale_x_discrete(labels = depth_labels) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
summary(aov(tmp$pco2_remos_ctd_temp ~ tmp$depth_group * tmp$montht))

@@

```{r, include=FALSE}
# First we prepare data. CT is needed for deconvolution
# we calculate it from at_calc and pCO2
# nuts are not taken into consideration
deconv_tmp <- d_all %>% # just for this chunk
  dplyr::select(datetime, monthd, sal_fb_mix, temp_fb, pco2_fb, at_calc) %>% 
  tidyr::drop_na()
deconv_tmp <- deconv_tmp %>% 
  dplyr::mutate(ct_calc = seacarb::carb(
    flag = 24, var1 = deconv_tmp$pco2_fb, var2 = deconv_tmp$at_calc*1e-6, S=deconv_tmp$sal_fb_mix, T=deconv_tmp$temp_fb, 
    Patm=1, P=1.1, Pt=0, Sit=0, 
    k1k2="l", kf="dg", ks="d", pHscale="T", b="l10")$DIC * 1e6
    )
deconv_monthly <-  deconv_tmp %>% 
  dplyr::group_by(monthd) %>% 
  dplyr::summarise(
    sal_fb_mix = mean(sal_fb_mix, na.rm = TRUE),
    temp_fb = mean(temp_fb, na.rm = TRUE),
    pco2_fb = mean(pco2_fb, na.rm = TRUE),
    at_calc = mean(at_calc, na.rm = TRUE),
    ct_calc = mean(ct_calc, na.rm = TRUE)
  ) %>% 
  dplyr::ungroup()

@@

```{r, fig.width=10, fig.height=10, echo=FALSE, message= FALSE, warning = FALSE}
# we calculate it from at_calc and pCO2
# nuts are not taken into consideration
tmp <- d_all %>% # just for this chunk
  dplyr::select(datetime, monthd, sal_fb_mix, temp_fb, pco2_fb, at_calc) %>% 
  tidyr::drop_na() %>% 
  dplyr::mutate(OmegaAragonite = seacarb::carb(
    flag = 24, var1 = pco2_fb, var2 = at_calc*1e-6, S=sal_fb_mix, T=temp_fb, 
    Patm=1, P=1.1, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T", b="l10")$OmegaAragonite)
summary(tmp$OmegaAragonite)
#plot
size_point <- 0.3 # size of data points
alpha <- 1 #transparency
size_labs <- 6 # font size labels
